A new type of generic, self-evolving and efficient automated deduction algorithm based on category theory

### 2023-04-28 resubmit/Math-7081-revised.tex
do the minor revision of the paper!

	To begin with, we use notation \(\mathcal{C}\) to demonstrate a category and use script\(\mathcal{F}\) to present a functor. \(\mathcal{U}\) stands for the Grothendieck universe selected and \(\mathcal{F}\mathit{o}\mathit{r}\) stands for the forgetful functor. A map is noted in one of the two following forms:

@@

	\noindent where \(A\) and \(B\) are sets and\(x\)and \(y\) are elements in \(A\) and \(B\).

@@

@@

	The definitions and theories presented in the paper utilizes the concepts of the category theory \cite{Li2019} and axiomatic set theory \cite{Li2019}. Therefore, readers are recommended to review understandings and conclusions about the two concepts before going over the paper.

@@

	\begin{equation}
		\mathcal{C}=\text{Sym}(\mathcal{C})\sqcup \text{Not}(\mathcal{C})\sqcup \text{Bra}(\mathcal{C})
	\end{equation}

	The three forms a partition of the big category.

>>>>

	To begin with, we use notation \(\mathcal{C}\) to demonstrate a category and use \(\mathcal{F}\) to present a functor. \(\mathcal{U}\) stands for the Grothendieck universe selected and \(\mathcal{F}_r\) stands for the forgetful functor. A map is noted in one of the two following forms:

@@

	\noindent where \(A\) and \(B\) are sets and \(x\) and \(y\) are elements in \(A\) and \(B\).

@@

	We use symbol \(On\) as the ordinal class composed by ordinals \cite{Li2019} such as \(\{\emptyset\}\) and infinite ordinal \(\omega\) which is defined as the inductive set supported by the Axiom of Infinity in ZFC. Note that \(On\) is a proper class instead of a set, otherwise it will lead to the Burali-Forti paradox.

	Additionally, we use \(S_p\) with \(S\) being a set and \(p\) being a statement about elements in \(S\) to represent subset \(\{x\in S|p(x)\equiv T\}\). For example, notation \(\mathbb{Z}_{>1}\) represents the set of integers greater than 1. Moreover, we utilized \(On_{\geq n}\) to represent ordinals not smaller than \(n\).

@@

	The definitions and theories presented in the paper utilizes the concepts of the category theory \cite{Li2019}, the ordinal theory \cite{Li2019} and axiomatic set theory \cite{Li2019}. Therefore, readers are recommended to review understandings and conclusions about these concepts before going over the paper.

@@

	\begin{equation}
		\mathcal{C}=\text{Sym}(\mathcal{C})\cup \text{Not}(\mathcal{C})\cup \text{Bra}(\mathcal{C})
	\end{equation}

	The formula above specifies that the meta category \(\mathcal{C}\) is the union set of the symbol subcategory, the notation subcategory and the bracket subcategory. It should be noted that though we will separately manipulate on \(\text{Sym}(\mathcal{C})\), \(\text{Not}(\mathcal{C})\) and \(\text{Bra}(\mathcal{C})\) afterwards, the annotation \(\mathcal{C}\) is still used to represent these subcategories serve for a common context.
